---
title: "Parent’s Choice or School’s Choice? Discrimination Against Students in Admission to Private, Charter, and Traditional Public Schools"
# subtitle: "Parent’s Choice or School’s Choice? "
author: |
  Patrick Button<sup>1</sup>, Hussain Hadah<sup>1,2</sup>, Douglas Harris<sup>1</sup>, Barbara Lundebjerg<sup>1</sup>
  <br>
  <div style="text-align: center; font-size: 0.8em; margin-top: 10px;">
  <sup>1</sup>Economics Department, Tulane University, <sup>2</sup>The Murphy Institute
  </div>


date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "assets/tulane-fonts.css", "assets/tulane.css"]
    self_contained: false # if true, fonts will be stored locally
    seal: true # show a title slide with YAML information
    includes:
      in_header: "assets/mathjax-equation-numbers.html"
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' # alternatives '16:9' or '4:3' or others e.g. 13:9
      navigation:
        scroll: false # disable slide transitions by scrolling
---
layout: true
<div style="position: absolute;left:20px;bottom:5px;color:black;font-size: 12px;">Hussain Hadah (Tulane/Murphy Institute) | Parent’s Choice or School’s Choice?  | `r format(Sys.time(), '%d %B %Y')`</div>

<!--- `r rmarkdown::metadata$subtitle` | `r format(Sys.time(), '%d %B %Y')`-->

---

```{r, load_refs, echo=FALSE, cache=FALSE, message=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           cite.style = 'authoryear', 
           style = "markdown",
           hyperlink = FALSE, 
           dashed = FALSE)
myBib <- ReadBib("assets/example.bib", check = FALSE)
top_icon = function(x) {
  icons::icon_style(
    icons::fontawesome(x),
    position = "fixed", top = 10, right = 10
  )
}
```

```{r setup, include=FALSE}
# xaringanExtra::use_scribble() ## Draw on slides. Requires dev version of xaringanExtra.

options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=4, fig.width=6,
  out.width="748px", out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=F#, echo=F, warning=F, message=F
  )
```


```{r, cache=FALSE, message=FALSE, warning=FALSE, include=TRUE, eval=TRUE, results=FALSE, echo=FALSE, tidy.opts = list(width.cutoff = 50), tidy = TRUE}
## Load and install the packages that we'll be using today
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tictoc, parallel, pbapply, future, future.apply, furrr, RhpcBLASctl, memoise, here, foreign, mfx, tidyverse, hrbrthemes, estimatr, ivreg, fixest, sandwich, lmtest, margins, vtable, broom, modelsummary, stargazer, fastDummies, recipes, dummy, gplots, haven, huxtable, kableExtra, gmodels, survey, gtsummary, data.table, tidyfast, dtplyr, microbenchmark, ggpubr, tibble, viridis, wesanderson, censReg, rstatix, srvyr, formatR, sysfonts, showtextdb, showtext, thematic, sampleSelection, RefManageR, DT, googleVis)
# devtools::install_github("thomasp85/patchwork")
remotes::install_github("mitchelloharawild/icons")
remotes::install_github("ROpenSci/bibtex")

# devtools::install_github("ajdamico/lodown")
## My preferred ggplot2 plotting theme (optional)
## https://github.com/hrbrmstr/hrbrthemes
# scale_fill_ipsum()
# scale_color_ipsum()
font_add_google("Fira Sans", "firasans")
font_add_google("Fira Code", "firasans")

showtext_auto()

theme_customs <- theme(
  text = element_text(family = 'firasans', size = 16),
  plot.title.position = 'plot',
  plot.title = element_text(
    face = 'bold', 
    colour = thematic::okabe_ito(8)[6],
    margin = margin(t = 2, r = 0, b = 7, l = 0, unit = "mm")
  ),
)

colors <-  thematic::okabe_ito(5)

# theme_set(theme_minimal() + theme_customs)
theme_set(hrbrthemes::theme_ipsum() + theme_customs)
## Set master directory where all sub-directories are located
mdir <- "/Users/hhadah/Dropbox/Research/My Research Data and Ideas/Identification_Paper"

## Set working directories
## Set working directory
mdir <- "~/Library/CloudStorage/Box-Box/education-audit-study"
rawdatadir  <- paste0(mdir,"/data/raw")
datasets  <- paste0(mdir,"/data/datasets")

## Set working directory

# COLOR PALLETES
library(paletteer) 
# paletteer_d("awtools::a_palette")
# paletteer_d("suffrager::CarolMan")

### COLOR BLIND PALLETES
#paletteer_d("colorblindr::OkabeIto")
#paletteer_d("colorblindr::OkabeIto_black")
# paletteer_d("colorBlindness::paletteMartin")
# paletteer_d("colorBlindness::Blue2DarkRed18Steps")
# paletteer_d("colorBlindness::SteppedSequential5Steps")
# paletteer_d("colorBlindness::PairedColor12Steps")
# paletteer_d("colorBlindness::ModifiedSpectralScheme11Steps")
colorBlindness <- paletteer_d("colorBlindness::Blue2Orange12Steps")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# scale_colour_paletteer_d("colorBlindness::ModifiedSpectralScheme11Steps", dynamic = FALSE)
# To use for fills, add
  scale_fill_manual(values="colorBlindness::Blue2Orange12Steps")

# To use for line and point colors, add
  scale_colour_manual(values="colorBlindness::Blue2Orange12Steps")
  #<a><button>[Click me](#sources)</button></a>
```

```{css, echo=F}
    /* Table width = 100% max-width */

    .remark-slide table{
        width: auto !important; /* Adjusts table width */
    }

    /* Change the background color to white for shaded rows (even rows) */

    .remark-slide thead, .remark-slide tr:nth-child(2n) {
        background-color: white;
    }
    .remark-slide thead, .remark-slide tr:nth-child(n) {
        background-color: white;
    }
```
## School Choice Programs are Expanding Rapidly

- #### Education is strongly linked to economic mobility and non-economic benefits .tiny[.gray[*(Chetty et al., 2014, 2016)*]]

- #### Minoritized groups face significant barriers .tiny[.gray[*(e.g., Bergman & McFarlin, 2020)*]]

- #### While public and charter schools are available to all, there are still inequalities through:

  - .font70[Resource and teacher quality imbalances .tiny[.gray[*(Ferguson, 1991, Johnson, 2019; Soss et al., 2012)*]]]
  - .font70[Larger class sizes .tiny[.gray[(Boozer & Rouse, 2001)]]]

--
- #### Then there are private schools

  - .font70[Less affirming of minoritized groups and less accessible]
  - .font70[They can legally discriminate on any basis except race .tiny[.gray[*(Petrilli, 2017)*]]]

---
## American education is undergoing one of its most significant shifts in the last half-century 

- #### 8 states have universal voucher .gray[.tiny[*(EdChoice, 2024)*]]

- #### Some argue that this would expand educational opportunities for low-income families

- #### Some research calls this into question .gray[.tiny[*(Harris, 2018a, forthcoming)*]]

- #### Milton Friedman (1955) popularized vouchers in the wake of Brown v. Board of Education

  - .font60[He tried to sell it knowing that southern states would use it to continue segregation]
  - .font60[Recent evidence affirms this interpretation .tiny[.gray[*(DeAngelis et al., 2019)*]]]

- #### Voucher expansion aligns with broader discriminatory policy trends (e.g., anti-DEI, anti-CRT, etc.)

--
- #### .brand-crawfest[To what extent do these programs discriminate against students is an open question]


---
## We will conduct an audit experiment of .brand-crawfest[public], .brand-crawfest[charter], and .brand-crawfest[private] schools in the US

- We will send emails to receive admission information

- We will randomize several characteristics of the students to test for discrimination

  - .brand-crawfest[*Race and Ethnicity:*] Black, Hispanic, White, Arab
  - .brand-crawfest[*LGBTQ+ Status:*] gay/lesbian vs. presumed straight and transgender vs. presumed cis
  - *Disability Status:* ADHD, autism, no disability disclosed
  - *Academic achievement:* High vs low
  - *Socioeconomic Status (SES)/Income:* Ph.D. vs. MD vs. no mention

---
## We contribute to the literature in several ways

- ##### We will be the first audit study to test for discrimination in access to education in .brand-crawfest[public], .brand-crawfest[charter], and .brand-crawfest[private] schools
  - .font70[No previous audit studies included private schools]

- ##### First study to test for a wide range of characteristics
  - .font70[LGBTQ+ and Arab]

- ##### We will also test how some policies will influence discrimination
  - .font70[DEI/CRT bans and LGBTQIA+ policies]

- ##### Determining where discrimination occurs and informing policy to counteract it
  - .font70[Testing mechanisms (e.g., statistical discrimination, implicit bias)  ]
  - .font70[Spatial/school-level charachteristics , such as district characteristics, segregation, and social views]


---
class: segue-yellow
background-image: url("assets/TulaneLogo.svg")
background-size: 20%
background-position: 95% 95%
count:false

# Data

---
## National Longitudinal School Database (NLSD)

- ### NLSD is a census of all schools in the US

  - Includes all private, charter, and traditional public schools from 1990-2019
  - Developed by Co-I Harris

- ### We will supplement the NLSD with data about voucher participation, discrimination law (e.g., anti-trans / anti-CRT / anti-DEI), and other socio-economic and demographic data of the state

- ### We will also supplement NLSD with data on school point of contact, from MDR Education dataset

---
## Summary Statistics from the NLSD

```{r, eval=TRUE, warning=FALSE, message=FALSE, echo=FALSE}
# Read data
NLSD <- read_csv(file.path(datasets,"NLSD_2019_2020.csv")) 

# Calculate school type counts
school_type_counts <- NLSD |>
  count(school_type) |>
  arrange(school_type)

# Get total sample size
total_n <- nrow(NLSD)

# Prepare data
variables_to_summarize <- c(
  "p_bl", "p_hp", "p_wh", "p_am", "p_as", "p_pc", "p_tr", "p_ot",
  "fte", "cs_mn_avg_ol",
  "bg_med_hh_inc_2000", "bg_perc_poverty_2000"
)

NLSD <- NLSD |> 
  select(school_type, all_of(variables_to_summarize)) |>
  mutate(
    school_type = as.factor(school_type),
    # Convert proportions to percentages
    p_bl = p_bl * 100,
    p_hp = p_hp * 100,
    p_wh = p_wh * 100,
    p_am = p_am * 100,
    p_as = p_as * 100,
    p_pc = p_pc * 100,
    p_tr = p_tr * 100,
    p_ot = p_ot * 100
  )

# Modify school_type factor levels to include sample sizes
NLSD <- NLSD |>
  mutate(
    school_type_with_n = case_when(
      school_type == "Catholic" ~ paste0("Catholic\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Catholic"], big.mark = ","), ")"),
      school_type == "Charter" ~ paste0("Charter\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Charter"], big.mark = ","), ")"),
      school_type == "Nonsectarian" ~ paste0("Nonsectarian\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Nonsectarian"], big.mark = ","), ")"),
      school_type == "Other religious" ~ paste0("Other Religious\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Other religious"], big.mark = ","), ")"),
      school_type == "Public" ~ paste0("Public\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Public"], big.mark = ","), ")"),
      TRUE ~ as.character(school_type)
    ),
    # Reorder factor levels: Private schools first, then Charter, then Public
    school_type_with_n = factor(school_type_with_n, levels = c(
      paste0("Nonsectarian\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Nonsectarian"], big.mark = ","), ")"),
      paste0("Catholic\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Catholic"], big.mark = ","), ")"),
      paste0("Other Religious\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Other religious"], big.mark = ","), ")"),
      paste0("Charter\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Charter"], big.mark = ","), ")"),
      paste0("Public\n(N = ", format(school_type_counts$n[school_type_counts$school_type == "Public"], big.mark = ","), ")")
    ))
  )

# Create the table with corrected syntax
datasummary(
  (`% Black` = p_bl) +
  (`% Hispanic` = p_hp) +
  (`% White` = p_wh) +
  (`% Asian` = p_as) +
  (`FTE Teachers` = fte) +
  (`Mean Achievement (Math & RLA)` = cs_mn_avg_ol) +
  (`Median HH Income (1999 $)` = bg_med_hh_inc_2000) +
  (`% in Poverty` = bg_perc_poverty_2000) ~ 
    Mean + SD + Factor(school_type_with_n) * (Mean + SD),
  data = NLSD,
  fmt = function(x) {
    # Check if it's income (large numbers)
    if (any(x > 1000, na.rm = TRUE)) {
      format(round(x, 0), big.mark = ",")
    } else {
      sprintf("%.1f", x)
    }
  },
  output = "gt"
) |>
  # Add column spanner for Full Sample columns
  gt::tab_spanner(
    label = paste0("Full Sample (N = ", format(total_n, big.mark = ","), ")"),
    columns = 2:3
  ) |>
  # Add spanner for Private schools
  gt::tab_spanner(
    label = paste0("Private (N = ", format(
      sum(school_type_counts$n[school_type_counts$school_type %in% c("Nonsectarian", "Catholic", "Other religious")], na.rm = TRUE), 
      big.mark = ","
    ), ")"),
    columns = 4:9  # Covers the 6 columns for the 3 private school types (Mean + SD for each)
  ) |>
  # Keep simple column labels
  gt::cols_label(
    Mean = "Mean",
    SD = "SD"
  ) |>
  # Add table title
  #gt::tab_header(
  #  title = "Table 3: Summary Statistics from the National Longitudinal School Database (NLSD)"
  #) |>
  # Add your specific table notes
  gt::tab_source_note(
    source_note = "Notes: The unit of observation is the school year from the 2019-2020 school year. The sample includes schools with an average of 20 or more students. Mean achievement represents the average academic achievement of students, measured through standardized test scores in mathematics and Reading Language Arts (RLA) for grades 3 through 8. The scores are standardized using the National Assessment of Educational Progress (NAEP) to allow comparisons across states, with data pooled across school years from 2008-09 to 2017-18. Higher values indicate better academic performance relative to the national standard and is only available for public schools."
  ) |>
  gt::tab_source_note(
    source_note = "Source: Authors' calculations based on the National Longitudinal School Database."
  )

```

---
class: segue-yellow
background-image: url("assets/TulaneLogo.svg")
background-size: 20%
background-position: 95% 95%
count:false

# Study Design

---
name: design

## We will consider many dimensions

.pull-left[
- #### At least 7 types of schools
  
  - .font70[**Private**: Catholic, Protestant, secular, and single-sex]
  - .font70[**Charter**: No-excuses/other, district/other authorizer]
  - .font70[**Traditional public schools**]
]

.pull-right[
- #### 6 dimensions of potential discrimination

  - .font70[**Race and ethnicity** (Black, Hispanic, White, Arab) signaled through names .font50[[[Race and ethnicity signals]](#race-ethnicity-names)]]
  - .font70[**LGBTQ+ status** (lesbian, gay, trans girls and boys, non-binary)]
  - .font70[**Disability status** (ADHD, autism, no disability disclosed)]
  - .font70[**Academic achievement** (high vs. low)]
  - .font70[**Socioeconomic status** (Ph.D., MD, no mention)]
]

- We will assign each school to either the sexual orientation and gender identity (SOGI)---high schools only---or the disability treatment arms .right[.small[[[Treatment arms info]](#treat-arms)]]

---
name: email-template

## Audit Study Email Template

**From:** [MOTHER'S FIRST AND LAST NAME] (<email address>)  
**Subject:** [EMAIL SUBJECT]

**Email Body:**
[GREETING],

[RECENTLY MOVED, RESEARCHING SCHOOLS] for our {daughter/son/child}, [CHILD's FIRST NAME].  
{She/He/They} [IS IN] [GRADE] and [HAS ACADEMIC PERFORMANCE]*.

| **If assigned a disability:** | **If assigned to be LGBT:** | **Otherwise:** |
|:-----|:-----|:-----|
| [{She/He} is on the spectrum and will need to be taught in a separate classroom.] (50%) **OR** [{She/He} has an IEP for {her/his} ADHD.] (50%) | [She is trans] (25%) **OR** [He is trans] (17%) **OR** [They are non-binary] (18%) **OR** [She is lesbian] (20%) **OR** [He is gay] (20%)] and we are hoping to find a school that is LGBT friendly. | No additional sentence. |

[APPLICATION QUESTIONS]

[VALEDICTION],  
[MOTHER'S FIRST AND LAST NAME] (50%) **OR** Dr. [" "], MD (25%) **OR** Dr. [" "], PhD (25%)

.right[.small[[[SOGI treatment arm]](#sogi-treatment)] .small[[[Disability treatment arm]](#disability-treatment)] .small[[[Academic achievement, SES, and voucher info]](#academic-achievement)]]

---
name: coding-response

## Coding response data

- ### Primary outcome: positive response

  - It will be coded as 1 if the school responds to our email in a way that is helpful (e.g., answers a question) or encouraging within two weeks and 0 otherwise

- ### Secondary outcome: Features of (un)helpful and discriminatory responses through qualitative thematic coding and large language models (LLMs) 

- ### Going beyond most audit studies which usually only consider response rates

.right[.small[[[School communication]](#communication-schools)] .small[[[Emailing strategy]](#emailing-strategy)] .small[[[Regression models]](#regression-models)]]

---
class: tulane-blue
background-image: url(assets/TulaneLogo-white.svg)
background-size: 260px
background-position: 5% 95%
count:false

# Thank you!

.pull-right[.pull-down[

<a href="mailto:hhadah@tulane.edu">
.white[`r icons::fontawesome("paper-plane")` hhadah@tulane.edu]
</a>

<a href="https://hussainhadah.com/">
.white[`r icons::fontawesome("link")` https://hussainhadah.com/]
</a>

<a href="https://github.com/hhadah">
.white[`r icons::fontawesome("github")` @hhadah]
</a>

<br><br><br>

]]

---
class: segue-yellow
background-image: url("assets/TulaneLogo.svg")
background-size: 20%
background-position: 95% 95%
count:false

# Appendix

---
name: treat-arms
count: false

## Assigning treatment arms

- ### We will assign each school to either the sexual orientation and gender identity treatment arms (65%) or the disability treatment arm (35%)

  - We randomize these separate treatment arms to avoid detection
  - Signaling SOGI is unusual for younger children
  - We want to avoid signaling too many uncommon characteristics in the same email
  - We also want to avoid signals that could complicate the interpretation of the results

.right[.small[[[Back]](#design)]]

---
name: race-ethnicity-names
count: false

## We will use names to signal race and ethnicity

- ### The names have been tested by Gaddis (2022; White, African American, and Hispanic names) and Baert, Lippens & Van Borm (2022; Arab) 

- ### We will assign a different race and ethnicity to each family in our email pairs:

  - Emails assigned to the disability treatment: probabilities 33% White, 23% Black, 23% Hispanic, and 21% Arab

  - Emails assigned to the SOGI treatment: probabilities 40% White, 30% Black, and 30% Hispanic

.right[.small[[[Back]](#design)]]


---
name: sogi-treatment
count: false

## Signaling sexual orientation or gender identity

- ### We will only use high school for this treatment arm

- ### When we do signal SOGI, the mother’s email mentions that the child is either gay (20%), lesbian (20%), transgender (15% trans girl, 15% trans boy), or non-binary (10%) by adding

  - "[He/She/They] [is/are] [gay/lesbian/trans], and we are hoping to find a school that is [supportive / LGBT friendly]" 
  - Mirroring language used in Pfaff et al. (2021) of religious beliefs

.right[.small[[[Back]](#email-template)]]

---
name: disability-treatment
count: false

## Signaling disability status

- ### For schools assigned to the disability treatment arm we will randomly assign the child to have:

  - Equal probabilities of ADHD  or autism
  - The remaining emails will not mention a disability

- ### We will add a sentence: 

  - "[She/he] has an IEP for [her/his] ADHD"
  - "[She/he] is on the spectrum and will need to be taught in a separate classroom"

.right[.small[[[Back]](#email-template)]]

---
name: academic-achievement
count: false

## Signaling academic achievement, socioeconomic status (SES), and voucher

- ### We will signal academic achievement by mentioning that the child:

  - "typically gets As and Bs"
  - "typically gets Cs"

- ### We will signal SES by either including or omitting degree information like "MD" or "PhD" in the mother’s email signature

- ### For schools that accept vouchers, we will include signals of voucher eligibility 

.right[.small[[[Back]](#email-template)]]

---
name: communication-schools
count: false

## Communication with the Schools 

- There is an extensive literature on how to write the emails to the schools (Patrick is the expert)


- We will send two emails to school administrators (available in the MDR Education data)


- We will randomize the characteristics of the students in the emails to signal our dimensions of interest


- The emails will be realistic and will ask for information about the admissions process

  - We will use some of Doug's extensive contacts with educators to ensure the emails are realistic

.right[.small[[[Back]](#coding-response)]]

---
name: emailing-strategy
count: false

## Emailing Strategy

- ### We will send two emails to each school

  - One email will be "treatment" (e.g. parent mention their child is transgender) and the other will be "control" (no mention)
  - We will randomize the order of the emails
  - Send at least one month apart

- ### Sending two emails substantially increases statistical power

.right[.small[[[Back]](#coding-response)]]

---
name: regression-models
count: false


## Short regression model

We will estimate a linear probability model (LPM) called the "short" model (following Muralidharan, Romero & Wüthrich, 2019):

$$
\begin{align*}
PositiveResponse_{i} &= \beta_1 Black_{i} + \beta_2 Hispanic_{i} + \beta_3 Arab_{i} + \beta_4 LGT_i + \beta_5 Disability_i \\
&+ \beta_6 FemmeName_i + \beta_7 LowGrades_i + \beta_8 HighGrade_i + \beta_9 SESMD_i \\
&+ \beta_{10} SESPhD_i + EmailCongrols_i \beta_{11} + SchoolControls_i \beta_{12} + \epsilon_i
\end{align*}
$$

Where $i$ indexes each email:
- $PositiveResponse_{i}$ is a binary outcome variable for receiving a positive response
- $Black_{i}$, $Hispanic_{i}$, and $Arab_{i}$ are indicator variables for race and ethnicity
- $LGT_i$ is an indicator variable for lesbian, gay, trans, or non-binary students
- $Disability_i$ is an indicator variable for students with ADHD or autism
- $FemmeName_i$ is an indicator variable for a feminine name

.right[.small[[[Back]](#coding-response)]]

---
name: regression-models-continued
count: false

## Short regression model (continued)

$$
\begin{align*}
PositiveResponse_{i} &= \beta_1 Black_{i} + \beta_2 Hispanic_{i} + \beta_3 Arab_{i} + \beta_4 LGT_i + \beta_5 Disability_i \\
&+ \beta_6 FemmeName_i + \beta_7 LowGrades_i + \beta_8 HighGrade_i + \beta_9 SESMD_i \\
&+ \beta_{10} SESPhD_i + EmailCongrols_i \beta_{11} + SchoolControls_s \beta_{12} + \epsilon_i
\end{align*}
$$

Where $i$ indexes each email and $s$ indexes each school:
- $LowGrades_i$ and $HighGrades_i$ are indicator variables for low and high academic achievement
- $SESMD_i$ and $SESPhD_i$ are indicator variables for high socioeconomic status (SES) parents with MD or PhD degrees
- $EmailControls_i$ includes indicator variables for different randomized email features,  and controls for email timing
- $SchoolControls_s$ which includes state fixed effects and school characteristics from the NLSD

.right[.small[[[Back]](#coding-response)]]


```{r gen_pdf, include = FALSE, cache = FALSE, eval = TRUE}
library(renderthis)
# https://hhadah.github.io/jpal-presentation/hadah-jpal-presentation.html

to_pdf(from = "~/Documents/GiT/jpal-presentation/hadah-jpal-presentation.html", 
       to = "~/Documents/GiT/jpal-presentation/hadah-jpal-presentation.pdf")
to_pdf(from = "~/Documents/GiT/jpal-presentation/hadah-jpal-presentation.html")
```
